Toronto's Most Studious Wards:  An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Prior to and Post-COVID

### 2024-01-25 outputs/paper/paper.qmd
Update paper

The Data section of this report aims to discuss the characteristics of the data sets used in addition to the methods of cleaning applied in order to get workable data. Succeeding, the Results section highlights trends and patterns discovered in statistical and graphical analysis. The Discussion section notes possible analytical limitations and measurement errors in the data sets in addition to overall insights of the report’s analysis. To summarize the report’s content, the Conclusion section briefly touches on the overall insights that can be distilled

## Data
Data used in this report were taken from the Open Data Toronto Online Portal [@opendatatoronto]. The specific data sets sourced from Open Data Toronto included *Library Branch General Information* [@librarybranch], *Library Circulation* [@circulationdata], and *Library Visits* [@visitdata]. The data sets were imported into RStudio where the open-source statistical programming language, R [@citeR], was used for cleaning and analysis. The raw data sets were extracted and saved with functionalities of the ‘readr’ [@readr] package. Data cleaning was aided by the use of the `janitor` [@janitor], `tidyverse` [@tidyverse], and `dplyr` [@dplyr] packages. To create tables and graphs for data visualization of the datasets, the `ggplot2` [@ggplot2] and `knitr` [@knitr] packages were used.

@@

## Results
Bar graphs were created with `ggplot2` to visualize the cleaned data sets. A bar graph for each year between 2018 and 2022 showing the total circulation by each ward was created. The y-axis scale for all of these graphs started at 0 and ended at 1600000 with increments increasing by 200000 to capture all data values. Additionally, a bar graph for each year between 2018 and 2022 showing the total visits to libraries by each ward was created. The y-axis scale for all of these graphs started at 0 and ended at 2400000 with increments increasing by 200000 to capture all data values.

>>>>

The Data section of this report aims to discuss the characteristics of the data sets used in addition to the methods of cleaning applied in order to get workable data. Succeeding, the Results section highlights trends and patterns discovered in statistical and graphical analysis. The Discussion section notes possible analytical limitations and measurement errors in the data sets in addition to overall insights of the report’s analysis. To summarize the report’s content, the Conclusion section briefly touches on the overall insights that can be distilled.

## Data
Data used in this report were taken from the Open Data Toronto Online Portal [@opendatatoronto]. The specific data sets sourced from Open Data Toronto included *Library Branch General Information* [@librarybranch], *Library Circulation* [@circulationdata], and *Library Visits* [@visitdata]. The data sets were imported into RStudio where the open-source statistical programming language, R [@citeR], was used for cleaning and analysis. The raw data sets were extracted and saved with functionalities of the `readr` [@readr] package. Data cleaning was aided by the use of the `janitor` [@janitor], `tidyverse` [@tidyverse], and `dplyr` [@dplyr] packages. To create tables and graphs for data visualization of the datasets, the `ggplot2` [@ggplot2] and `knitr` [@knitr] packages were used.

@@

## Results
Bar graphs were created with `ggplot2`[@ggplot2] to visualize the cleaned data sets. A bar graph for each year between 2018 and 2022 showing the total circulation by each ward was created. The y-axis scale for all of these graphs started at 0 and ended at 1600000 with increments increasing by 200000 to capture all data values. Additionally, a bar graph for each year between 2018 and 2022 showing the total visits to libraries by each ward was created. The y-axis scale for all of these graphs started at 0 and ended at 2400000 with increments increasing by 200000 to capture all data values.
